|

### 2021-12-03 paper/dcpo_demsupport.Rmd
confirmed the new datasets

```{r data-input, include=FALSE, cache=TRUE}
## Replication data
load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/2hwqg/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/wfm3c/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/rvc92/download
load(here("data", "exp_claassen_input.rda")) # Source???

>>>>

```{r data-input, include=FALSE, cache=TRUE, cache.extra = tools::md5sum(here::here("output", "estimates_moc_correctAJPS.RDS"))}
## Replication data
load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/2hwqg/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/wfm3c/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/rvc92/download
load(here("data", "exp_claassen_input.rda")) # Source???
